Rapid technological progress in white light-emitting diodes and its sources in innovation and technology spillovers

### 2023-08-13 2_SSL_NE/article/article_main.tex
added edits

\begin{abstract}
  Since their introduction in 1996, white LEDs have greatly improved in performance, efficiency, and manufacturing cost. These advancements are crucial for reducing carbon emissions as lighting accounts for nearly 20\% of global electricity consumption. Studying the rapid progress in LED technology can provide valuable insights for accelerating innovation in other clean energy technologies. However, the extent and sources of these improvements have not been systematically investigated. Through cost and performance modeling, along with expert interviews, we found that the efficiency of top-performing warm white LED packages increased from 5.8\% in 2003 to 38.8\% in 2020. Additionally, the manufacturing cost of low-to-mid-power LED packages decreased from \$1.1 to \$0.05 (in 2020 USD) between 2003 and 2020, a 95.5\% decrease. Technology spillovers from other sectors contributed to 8.5\% of efficiency improvements and nearly 100\% of consumer experience enhancements, playing a crucial role in widespread LED adoption.
\end{abstract}

@@

A rapid reduction of global carbon dioxide emissions is urgently required in order to mitigate the effects of climate change \cite{Forster2019}. According to the United Nations, by the end of 2021, more than 130 countries have set or are considering setting a net zero emissions target by 2050 \cite{un2021climate}. The European Union, for example, has set a target of net zero emissions by 2050. It aims to meet this goal with the help of the European Green Deal, alongside other EU and national policies \cite{eu2020green}. The United Kingdom similarly has adopted a national strategy to achieve net-zero by 2050 \cite{noauthor_ieairena_2023}.

Achieving these ambitious and critically important targets will require both the deployment of new clean energy technologies, and the acceleration of innovation in existing supply-side \cite{sinn2012green} and demand-side energy technologies \cite{rgeVorsatz2009}. To ensure rapid adoption of these technologies, significant reductions in their costs and improvements in their performance and consumer experience are needed. This requires understanding how these cost reductions and performance improvements can be achieved \cite{Stephan2021,Ziegler2021}.

>>>>

\begin{abstract}
  Since their introduction to the market in 1996, white light-emitting diodes (LEDs) have greatly improved in performance, efficiency, and manufacturing cost. These advancements have been crucial for reducing global carbon emissions in the lighting sector which accounts for nearly 20\%  of global electricity consumption. Understanding the extent and sources of the rapid progress in white LED technology can thus provide valuable insights for accelerating innovation in other demand-side clean energy technologies. Through cost and performance modeling, literature review, patent analysis, and expert interviews, we find that the efficiency of top-performing  warm white GaN-based  LED packages increased from 5.8\% in 2003 to 38.8\% in 2020. Over the same period, the manufacturing cost of low-to-mid-power LED packages decreased by 95.5\% from \$1.1 to \$0.05 (in 2020 USD). Technology spillovers from other sectors contributed to 8.5\% of efficiency improvements and nearly all consumer experience enhancements, playing an important role in widespread LED adoption in lighting.
\end{abstract}

@@

A rapid reduction of global carbon dioxide emissions is urgently required in order to mitigate the effects of climate change \cite{Forster2019}. According to the Net Zero Tracker Database, by the end of 2023, more than 150 countries have set or are considering setting a net zero emissions target by 2050 \cite{zerotracker}. The European Union, for example, has set a target of net zero emissions by 2050. It aims to meet this goal with the help of the European Green Deal, alongside other EU and national policies \cite{eu2020green}. The United Kingdom similarly has adopted a national strategy to achieve net-zero by 2050 \cite{noauthor_ieairena_2023}.

Achieving these ambitious and critically important targets will require both the deployment of new clean energy technologies \cite{iea2020cleanenergy}, and the acceleration of innovation in existing supply-side \cite{sinn2012green} and demand-side energy technologies \cite{rgeVorsatz2009}. To ensure rapid adoption of these technologies, significant reductions in their costs and improvements in their performance and consumer experience are needed. This requires understanding how these cost reductions and performance improvements can be achieved \cite{Stephan2021,Ziegler2021}.
